---
title: "Lab 01 - Hello R"
author: "Conor Lacey"
date: "01/12/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There are 1846 rows and 3 columns. The variables in the data include
the dataset variable, x variable, and y variable.

### Exercise 2


Plot of the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plot of the data in the star dataset:

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in the star dataset:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation of the star dataset is very similar to that of the dino dataset.
### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.



## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
